EGGs are adhesive!\\ An algebraic account of equality saturation

### 2025-09-25 jlamp/jlamp.tex
minima

For the sake of readability, all the proofs appear in the appendices. 
This work is an extended version of~\cite{uovadesive}.
With respect to the conference paper, the way term graphs
are described is completely changed: they are now presented 
as an instance of the newly introduced category of 
left-monogamous hypergraphs. Also the notion of separated 
hypergraphs is original, so that Sections 3.1.1 and 3.2.1 are largely new,
and consequently so Section 4.1.1, 4.2 and 5. 
%
Finally, also Section~6 on the applications of DPO rewriting has been rewritten 
and expanded, trying to highlight the nuances of its use.
%For the sake of completeness, 
%and in order to fix the notation, we prove all the results 
%recalled in the background section, besides those that are original 
%to our work.

>>>>

For the sake of readability, all the proofs appear in the appendices. 
This work is an extended version of~\cite{uovadesive}.
With respect to the conference paper, the way term graphs
are described is completely changed: they are now presented 
as an instance of the newly introduced category of 
left-monogamous hypergraphs. Also the notion of separated 
hypergraphs is original, so that Sections 3.1.1 and 3.2.1 are largely new,
and consequently so Sections 4.1.1, 4.2, and 5. 
%
Finally, also Section~6 on the use of DPO rewriting has been rewritten 
and expanded, trying to highlight the nuances of its application.
%For the sake of completeness, 
%and in order to fix the notation, we prove all the results 
%recalled in the background section, besides those that are original 
%to our work.
